\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
revise diagnosis model

	The purpose of Stage D2 is to output the disease probability vectors. For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images that are composed of one image for each of the target abnormities, and label the sets of images with the disease. We get 10000 sets of images for training and 10000 sets of images for testing for each of the disease.

@@

	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because they only consists of a FC layer.

@@

	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_conf_mat} shows the accuracies of the submodels of Stage D1. Table~\ref{tb:diagnosis_test} shows the predictive values of Stage D2, Fig.~\ref{fig:D2_ROC} shows the ROCs, Fig.~\ref{fig:D2_conf_mat} shows the confusion matrix and Fig~\ref{fig:D2_tSNE} shows the t-SNE graph.

	The submodels of Stage D1 tend to yield results one severity level higher or lower than the label. This impairs the accuracies of the submodels of Stage D1. However, Stage D2 partly solves this problem, as the model in Stage D2 has a higher accuracy than the average accuracy of the Stage D1 submodels.

>>>>

	The purpose of Stage D2 is to output the disease probability vectors. For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images where each of them is from one target abnormitiy, and label the sets of images with the disease. We get 10000 sets of images for training and 10000 sets of images for testing for each of the disease.

@@

	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because there are plenty of training data and the models leverage relatively simpler networks.

@@

	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_acc_bar} shows the accuracies of the submodels of Stage D1. Table~\ref{tb:diagnosis_test} shows the predictive values of Stage D2, Fig.~\ref{fig:D2_ROC} shows the ROCs, Fig.~\ref{fig:D2_conf_mat} shows the confusion matrix and Fig~\ref{fig:D2_tSNE} shows the t-SNE graph.

	The submodels of Stage D1 tend to yield results where the predicted severity level is 1 level offset from the label. This impairs the accuracies of the submodels of Stage D1. However, Stage D2 partly solves this problem, as the model in Stage D2 has a higher accuracy than the average accuracy of the Stage D1 submodels.
